March Madness Basketball Tournament

### 2021-04-17 slides/slides.Rmd
added citation
adding final slides

---
title: "March Madness Basketball Turniment"
author: "Sabrina Ball and Joe Despres"
date: "updated: `r Sys.Date()`"
output:
  xaringan::moon_reader:
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(fig.width=15,
                      fig.height=12, 
                      echo = FALSE, 
                      message = FALSE,
                      warning = FALSE, 
                      comment = "")

@@

>>>>

---
title: "March Madness Basketball Tournament"
author: "Sabrina Ball and Joe Despres"
date: "updated: `r Sys.Date()`"
output:
  xaringan::moon_reader:
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(fig.width=15,
                      fig.height=12, 
                      echo = FALSE, 
                      message = FALSE,
                      warning = FALSE, 
                      comment = "")

@@

# References

Faraway, Julian James. Extending the Linear Model with R:  Generalized Linear,    Mixed Effects and Nonparametric Regression Models.        Chapman &amp; Hall/CRC, 2016.
